DATA 621 - Business Analytics and Data Mining

### 2020-10-28 HW3/HW3-Group2.Rmd
Update HW3-Group2.Rmd
Added Intro

# DATA EXPLORATION
## Data Description
The training data set contains 466 records summarizing attributes of various
neighborhoods in the city of Boston. The response variable is coded such that it
is `1` when the neighborhood’s crime rate is above the median and `0` when it is
not. In all, there are 12 predictors. These include:

>>>>

# Introduction
Using data from a major city, Boston, we strove to identify trends and model 
crime rates and their affect on the housing conditions.  Using 
binary logistic regression models we hope to predict the crime levels in a 
neighborhood using various conditions to set the status of the neighborhood. 
Each section of the report breaks down the steps we took to achieve a solid 
and effective model.

# DATA EXPLORATION
## Data Description

The training data set contains 466 records summarizing attributes of various
neighborhoods in the city of Boston. The response variable is coded such that it
is `1` when the neighborhood’s crime rate is above the median and `0` when it is
not. In all, there are 12 predictors. These include:
